---
title: "README"
author: "Victoria Seng"
date: "11/17/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this?

This app allows the user to explore, model, and predict with online shopping data. Besides making visualizations, summaries, and exploring & exporting the data itself, the user can design and train three different kinds of predictive model for whether or not a shopper will generate revenue. They can then create a fictitious observation that will be evaluated via the model and its outcome predicted.

## Required Packages

The following packages are required for the app to function:

*  `Shiny`
*  `shinythemes`
*  `tidyverse`
*  `magrittr`
*  `fastDummies`
*  `caret`
*  `ranger`
*  `rpart`
*  `rpart.plot`
*  `DT`
*  `stringr`

### Install packages

Use the code below to install the required packages

```{r installPkg, eval = FALSE, echo = TRUE}
install.packages(c("shiny",
                   "shinythemes",
                   "tidyverse",
                   "magrittr",
                   "fastDummies",
                   "caret",
                   "ranger",
                   "rpart",
                   "rpart.plot",
                   "DT",
                   "stringr"
                   )
                 )
```

### Run App

Use the code below to run this app yourself:

```{r runGithubCode, eval = FALSE, echo = TRUE}
shiny::runGitHub(repo = "st558_project3", 
                 username = getOption("github.user"), 
                 ref = "main", 
                 subdir = "p3app", 
                 port = NULL, 
                 launch.browser = getOption("shiny.launch.browser", 
                                            interactive()
                                            )
                 )
```
